Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-25 latex/comp_or.tex
Paper 2 update
Pheromone update changed

		\Procedure{$ACLP+RPDP$}{$scenario,\ surplus,\ numProcs$}

@@

			\For {each $\pi \in S_K$} \label{main:loop1}
				\State $f_{\pi} \gets SolveTour(\pi, L, M, C, N, method, numProcs )$ \label{main:method}
			\EndFor \label{main:loop2}
			\State $answer[scenario,surplus,method] \gets \max f$ \label{main:f}
		\EndFor

@@

		\Procedure{$SolveTour$}{$\pi, L, M, C, N, method, numProcs$}

		\State $\pi(0) \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q_{\pi(k)}, E^Q_{\pi(k)}, M \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M \cup N_{\pi(k)} \cup Q_{\pi(k)}, E^Q_{\pi(k)})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M \gets SetPalletsDestination( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1, numProcs)$ \label{tour:node}
			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_2)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

@@

In this subsection we present implementations of $SolveNode(method,k, G)$, where $method$\/ corresponds to a heuristic, $k$\/ is the index of the current node and $G$\/ is the allocation graph of the consolidated items that remain on board at node $l_k$.

@@

$SolveNode(mpACO, k, G, numProcs)$ is the main process, while $AntSolve(G^+,\ AntsQueue,\ ga^k_{ij})$ is executed the child concurrent processes.

@@

		\Procedure{$SolveNode$}{$mpACO, k, G, numProcs$}

@@

				\While{$runtime < 0.7s$} \Comment{Wait until there is a solution in the queue}

@@

		\Procedure{$SolveNode$}{$mpShims, k, G, numProcs$}

>>>>

		\Procedure{$ACLP+RPDP$}{$scenario,\ surplus,\ numProcs,\ timeLim$}

@@

			\For {each $\pi \in S_K$} \label{main:loop1}
				\State $f_{\pi} \gets SolveTour(\pi, L, M, C, N, method, numProcs,\ timeLim )$ \label{main:method}
			\EndFor \label{main:loop2}
			\State $answer[scenario,surplus,method] \gets \max f$ \label{main:f}
		\EndFor

@@

		\Procedure{$SolveTour$}{$\pi, L, M, C, N, method, numProcs,\ timeLim$}

		\State $\pi(0) \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q_{\pi(k)}, E^Q_{\pi(k)}, M \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M \cup N_{\pi(k)} \cup Q_{\pi(k)}, E^Q_{\pi(k)})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M \gets SetPalletsDestination( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1, numProcs,\ timeLim)$ \label{tour:node}
			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_2)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

@@

In this subsection we present implementations of $SolveNode(...)$, where $method$\/ corresponds to a heuristic, $k$\/ is the index of the current node and $G$\/ is the allocation graph of the consolidated items that remain on board at node $l_k$.

@@

$SolveNode(mpACO, ...)$ is the main process, while $AntSolve(...)$ is executed the child concurrent processes.

@@

		\Procedure{$SolveNode$}{$mpACO, k, G, numProcs,\ timeLim$}

@@

				\While{$runtime < timeLim$} \Comment{Wait until there is a solution in the queue}

@@

		\Procedure{$SolveNode$}{$mpShims, k, G, numProcs,\ timeLim$}
